|

### 2023-02-15 paper.Rmd
autogit

The framework that was used to run all experiments of this thesis was provided by the supervisor of this thesis David Wittenberg and uses the python programming language [@python3] in conjunction with the baseline libraries `Keras` [@chollet2015keras] for deep neural networks and `deap` [@DEAP_JMLR2012] for evolutionary computation.
For data visualizations the python package `matplotlib` [@matplotlib] was used, statistical analysis and evaluations were conducted using primarily the data science libraries `scipy` [@scipy], `numpy` [@numpy] and `pandas` [@pandas].

@@

```{r statutory_declaration, echo=FALSE}
knitr::include_graphics("~/masterThesis/master_thesis/private/statutory_declaration_signed.pdf")
```

>>>>

The framework that was used to run all experiments of this thesis was provided by the supervisor of this thesis David Wittenberg and uses the python programming language [@python3] in conjunction with the baseline libraries `Keras` [@chollet2015keras] for deep neural networks and `deap` [@DEAP_JMLR2012] for evolutionary computation.
For data visualizations the python package `matplotlib` [@matplotlib] was used, statistical analysis and evaluations were conducted using primarily the data science libraries `numpy` [@numpy], `scipy` [@scipy] and `pandas` [@pandas].

@@

```{r statutory_declaration, echo=FALSE, fig.align = 'center', out.width='500px'}
knitr::include_graphics("~/masterThesis/master_thesis/private/statutory_declaration_signed.pdf")
```

### 2023-02-15 paper.tex
autogit

The framework that was used to run all experiments of this thesis was provided by the supervisor of this thesis David Wittenberg and uses the python programming language {[}\protect\hyperlink{ref-python3}{27}{]} in conjunction with the baseline libraries \texttt{Keras} {[}\protect\hyperlink{ref-chollet2015keras}{2}{]} for deep neural networks and \texttt{deap} {[}\protect\hyperlink{ref-DEAP_JMLR2012}{6}{]} for evolutionary computation.
For data visualizations the python package \texttt{matplotlib} {[}\protect\hyperlink{ref-matplotlib}{12}{]} was used, statistical analysis and evaluations were conducted using primarily the data science libraries \texttt{scipy} {[}\protect\hyperlink{ref-scipy}{30}{]}, \texttt{numpy} {[}\protect\hyperlink{ref-numpy}{8}{]} and \texttt{pandas} {[}\protect\hyperlink{ref-pandas}{25}{]}.

@@

\begin{center}\includegraphics{private/statutory_declaration_signed} \end{center}

>>>>

The framework that was used to run all experiments of this thesis was provided by the supervisor of this thesis David Wittenberg and uses the python programming language {[}\protect\hyperlink{ref-python3}{27}{]} in conjunction with the baseline libraries \texttt{Keras} {[}\protect\hyperlink{ref-chollet2015keras}{2}{]} for deep neural networks and \texttt{deap} {[}\protect\hyperlink{ref-DEAP_JMLR2012}{6}{]} for evolutionary computation.
For data visualizations the python package \texttt{matplotlib} {[}\protect\hyperlink{ref-matplotlib}{12}{]} was used, statistical analysis and evaluations were conducted using primarily the data science libraries \texttt{numpy} {[}\protect\hyperlink{ref-numpy}{8}{]}, \texttt{scipy} {[}\protect\hyperlink{ref-scipy}{30}{]} and \texttt{pandas} {[}\protect\hyperlink{ref-pandas}{25}{]}.

@@

\begin{center}\includegraphics[width=500px]{private/statutory_declaration_signed} \end{center}
